---
title: "QMM Assignment-6"
author: "Abhinay Chiranjeeth Marneni"
date: "2022-11-19"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading the packages
```{r}
library(lpSolve)
library(lpSolveAPI)
```

### Formulating Lp model problem
#S1 = shift 1 with Sunday 
#S2 = shift 2 with Monday 
#S3 = shift 3 with Tuesday 
#S4 = shift 4 with Wednesday 
#S5=  shift 5 with Thursday 
#S6 = shift 6 with Friday 
#S7 = shift 7 with Saturday 

# Objective function 
#Min: 775x1 + 800x2 + 800x3 + 800x4 + 800x5 + 775x6 + 750x7;
# Constraints 
#0x1 + 1x2 + 1x3 + 1x4 + 1x5 + 1x6 + 0x7 >= 18;
#0x2 + 0x2 + 1x3 + 1x4 + 1x5 + 1x6 + 1x7 >= 27;
#1x3 + 0x2 + 0x3 + 1x4 + 1x5 + 1x6 + 1x7 >= 22;
#1x4 + 1x2 + 0x3 + 0x4 + 1x5 + 1x6 + 1x7 >= 26;
#1x5 + 1x2 + 1x3 + 0x4 + 0x5 + 1x6 + 1x7 >= 25;
#1x6 + 1x2 + 1x3 + 1x4 + 0x5 + 0x6 + 1x7 >= 21;
#1x7 + 1x2 + 1x3 + 1x4 + 1x5 + 0x6 + 0x7 >= 19;
#S1 > 0;
#S2 > 0;
#S3 > 0;
#S4 > 0;
#S5 > 0;  
#S6 > 0;
#S7 > 0;
#int S1, S2, S3, S4, S5, S6, S7;

# Create table
```{r}
table <- make.lp(7, 7)
set.objfn(table, c(775, 800, 800, 800, 800, 775, 750))      # Objective function 
lp.control(table,sense='min')
set.row(table, 1, c(0, 1, 1, 1, 1, 1, 0), indices = c(1, 2, 3, 4, 5, 6, 7)) # Set LHS and RHS
set.row(table, 2, c(0, 0, 1, 1, 1, 1, 1), indices = c(1, 2, 3, 4, 5, 6, 7))
set.row(table, 3, c(1, 0, 0, 1, 1, 1, 1), indices = c(1, 2, 3, 4, 5, 6, 7))
set.row(table, 4, c(1, 1, 0, 0, 1, 1, 1), indices = c(1, 2, 3, 4, 5, 6, 7))
set.row(table, 5, c(1, 1, 1, 0, 0, 1, 1), indices = c(1, 2, 3, 4, 5, 6, 7))
set.row(table, 6, c(1, 1, 1, 1, 0, 0, 1), indices = c(1, 2, 3, 4, 5, 6, 7))
set.row(table, 7, c(1, 1, 1, 1, 1, 0, 0), indices = c(1, 2, 3, 4, 5, 6, 7))
rhs <- c(18, 27, 22, 26, 25, 21, 19)
set.rhs(table, rhs)
set.constr.type(table, c(">=", ">=", ">=", ">=", ">=", ">=", ">=")) ## constraint and variables
set.bounds(table, lower = rep(0, 7))
set.type(table, 1:7,"integer")
lp.rownames <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
lp.colnames <- c("S1", "S2", "S3","S4", "S5", "S6","S7")
dimnames(table) <- list(lp.rownames, lp.colnames)
table
```

#Solving AP-Hub lp model to find optimal variables of workers in factory.

```{r}
solve(table)
# Getting objective, variables
get.objective(table)
get.variables(table)
```
##The table shows the available workers, and the total cost is 25675.

#A week's worth of factory worker shifts are considered in order to figure out the best method for reduce total wage costs.
```{r}
shift<- matrix(c(0,4,5,0,8,1,0,0,0,5,0,8,1,13,2,0,0,0,8,1,13,2,4,0,0,8,1,13,2,4,5,0,0,1,13,2,3,4,0,0,0,13,2,4,5,0,8,0,0), ncol=7,byrow=TRUE)
row.names(shift) <- c('Sunday','Monday','Tuesday','Wednesday','Thursday','Friday','Saturday')
colnames(shift)<- c('Sun-Mon','Mon-Tues','Tues-Wed','Wed-Thur','Thur-Fri','Fri-Sat','Sat-Sun')
shift
rowSums(shift) #To reduce the total cost of labor expenses, the number of workers should be distributed according to each                      day's scheduled shift.
```