---
title: "QMM ASSIGMENT 3"
author: "Abhinay Chiranjeeth Marneni"
date: "2022-10-19"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Loading packages*
```{r}
library("lpSolve")
library("tinytex")
```
**1.Formulate and solve the Transportation Problem with R**
\vspace{2mm}
*Make a table by using information provided.*
```{r}
cost <- matrix(c(22,14,30,600,100,
                 16,20,24,625,120,
                 80,60,70,"-","-"), ncol=5,byrow=T)
colnames(cost) <- c("Warehouse1", "Warehouse2", "Warehouse3", "ProductionCost","ProductionCapacity")
rownames(cost) <- c("PlantA", "PlantB", "Demand")
cost <- as.table(cost)
cost
```  
\vspace{3mm}
**Primal Model**
\vspace{2mm}
**The Objective Function of Minimize the Transportation cost**

$$ Z = 622C_{11} + 614C_{12} + 630C_{13} + 0C_{14} + 641C_{21} + 645C_{22} + 649C_{23} + 0C_{24}$$\\

**The Constraints for Primal model**
**Subject to**
\vspace{2mm}

$${\text Supply \hspace{2mm} Constraints}$$
$$C_{11} + C_{12} + C_{13} + C_{14} \le 100$$
$$C_{21} + C_{22} + C_{23} + C_{24}\le 120$$
$${\text Demand \hspace{2mm} Constraints}$$
$$C_{11} + C_{21}\ge 80$$
$$C_{12} + C_{22}\ge 60$$
$$C_{13} + C_{23}\ge 70$$
$$C_{14} + C_{24}\ge 10$$
\vspace{2mm}
$${\text  Non - Negativity \hspace{2mm} Constraints} $$
$$C_{ij} \ge 0 \hspace{4mm} \text {Where i = 1,2 and j = 1,2,3,4} $$
# demand Constraints is not equal to supply variables 
# To solve Primal with R


```{r}
# Matrix for the given objective function
trans.cost <- matrix(c(622,614,630,0,
                 641,645,649,0), ncol=4, byrow=T) # Matrix for the given objective function
trans.cost
colnames(trans.cost) <- c("Warehouse1", "Warehouse2", "Warehouse3", "Dummy")
rownames(trans.cost) <- c("PlantA", "PlantB")
trans.cost
  
#Identify the row signs, row right hand side values, column sign and column right hand side values
row.signs <- rep("<=",2)
row.rhs <- c(100,120)
col.signs <- rep(">=",4)
col.rhs <- c(80,60,70,10)
lptrans.cost <- lp.transport(trans.cost,"min", row.signs,row.rhs,col.signs,col.rhs) #the linear problem transport function 
```

```{r}
# the objective value for linear problem transport function
  lptrans.cost$objval # the solution of primal 
```
\vspace{2mm}
$${\text Where \hspace{2mm} WH_1 = Warehouse \hspace{2mm} 1}$$
$$\hspace{2mm} WH_2 = Warehouse \hspace{2mm} 2$$
$$\hspace{2mm} WH_3 = Warehouse \hspace{2mm} 3$$
$${\text Where \hspace{2mm} PL_1 = PlantA \hspace{2mm}}$$
$$\hspace{2mm} PL_2 = plantB \hspace{2mm}$$

```{r}
#To Get the constraints value
lptrans.cost$solution
```
##The shipping cost from each plant to the warehouse of each wholesaler along with the monthly demand from each wholesaler are also indicated in the table

**2. Formulate the dual model of the above transportation problem**
\vspace{1mm}\newline

##the primal model to minimize the transportation cost the dual model of  maximize the value added(Z)

$$ {\text Maximize \hspace{3mm} Z = } \hspace{3mm} 80WH_1 + 60WH_2 + 70WH_3 - 100PL_1 - 120PL_2$$
\vspace{1mm}\newline
**Subject to the payment constraints**


$$ {\text Total \hspace{2mm} Payments \hspace{2mm} Constraints} $$
$$ WH_1 - PL_1 \ge 622 $$ 
$$ WH_2 - PL_1\ge 614$$
$$ WH_3 - PL_1 \ge 630$$
$$ WH_1 - PL_2 \ge 641$$
$$ WH_2 - PL_2 \ge 645$$
$$ WH_3 - PL_2 \ge 649$$
$$ WH_i > 0 , PL_j > 0$$
\newline
**3.Economic Interpretation**
**for above  Constraints we can written as**
$$WH_1 \le 622 + PL_1$$  
$$WH_2 \le 614 + PL_1 $$
$$WH_3 \le 630 + PL_1 $$
$$WH_1\le 641 + PL_2$$
$$WH_2 \le 645 + PL_2$$
$$WH_3 \le 649 + PL_2$$
$$ \text{Here Warehouse 1 recieved payment , which consider as marginal revenue}$$
$$ \text{To Maximization the Profit MR has to equal to MC , MR = MC}$$
$$ \text{We must lower plant expenses in order to get to the Marginal Revenue (MR)}$$
$$ \text{MR < MC}$$
$$ \text{We must expend more supply production in order to get to the Marginal Revenue (MR)}$$
$$ \text{MR > MC}$$