---
title: "Qmm Assignment-5"
author: "Abhinay Chiranjeeth Marneni"
date: "2022-11-06"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading the packages
```{r}
library(lpSolve)
library(lpSolveAPI)
```
## The objective function is Z = P-6C-3D 
## Where, P = total profit over the life of the new products
##C = change in the current level of employment
##D = decrease in next year’s earnings from the current year’s level.


# Where, xc1,xc2,xc3,yc1,yc2,yc3,yc4
## Let xc1 ,xc2 and xc3 be the number of products produced for Product 1,2 and 3
## yc1 = negative deviation or per unit decrease in employment level
## yc2 = Positive deviation or per unit increase in employment level
## yc3 = negative deviation or per unit decrease in goal regarding earnings next year
## yc4 = Positive deviation or per unit increase in goal regarding earnings next year

# Maximize profit which is given by 
# P = 20xc1 + 15xc2 +25xc3

# Formulation of constraints
## yc2 - yc1 = 6xc1 + 4xc2 + 5xc3 - 50    #Employment level constraint
##  yc4 - yc3 = 8xc1 + 7xc2 + 5xc3 - 75   #Earnings next year constraint


# Objective function  is:

## Maximize(Z): 20xc1 + 15xc2 + 25xc3 - 6yc1 - 6yc2- 3yc3

# Constraints:

## 6xc1 + 4xc2 + 5xc3 + yc1 - yc2 = 50
## 8xc1 + 7xc2 + 5xc3 + yc3 - yc4 = 75
   
   
# importing the "gp.lp" file data which show above 
```{r}
goal<- read.lp("gp.lp")
goal
```
# Table
```{r}
goal1<- matrix(c("Total Profit", "Employment Level", "Earnings Next Year",
                20,6,8,
                15,4,7,
                25,5,5,
                "Maximize","=50",">=75"),ncol=5, byrow = F)
                
colnames(goal1) <- c('Factor', 'Product1','Product2','Product3','Goal')
goal1


```

# Finding to get objective and variables values from above goal data file.
## Solving
```{r}
solve(goal)
get.objective(goal)
get.variables(goal)
```
# Interpretation

## 225 million dollars are the profit, which is  showing the problem's objective function.

## The constraint values are: xc1=0,xc2=0,xc3=15,yc1=0,yc2=25,yc3=0,yc4=0

## We can see from the above values of the constraints that xc1=0 and xc2=0, which means that expanding the number of units produced for Products 1 and 2 will not greatly impact total profit maximization.

## We can see expanding the number of units produced for Products 3 by xc3=15 can help in contributing to profit maximization.

## The employment level was to maintain as 50. Here, yc2=25 shows a positive departure, which converts into a rise in employment of 250 individuals. This will lead to a decrease in profit.

## The estimated values of yc3 and yc4 can be utilized to calculate the earnings for the next year. Here, both values are zero, showing neither the profits for the next year might rise or fall.


